---
title: "701 Assignment"
author: "Chaewon Jeong"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("ggpubr")
# install.packages("countrycode")

library(here)
library(tidyverse)
library(ggpubr)
library(countrycode)
```


```{r import, message=FALSE}
# Import datasets and pre-process
mbti <- read_csv(here("countries.csv"))
  # MBTI processing 1: change space to underbar
  # MBTI processing 2: Change column header: dash to underbar
  mbti <- mbti |> 
    rename_with(~ str_replace_all(., "-", "_")) |> 
    arrange(Country)

happy <- read_csv(here("world-happiness-report-2021.csv"))
  # Happy processing 1: change space to underbar
  # Happy processing 2: Order the country alphabetically
  happy <- happy |> 
    rename_with(~ str_replace_all(., " ", "_")) |> 
    arrange(Country_name)

literacy <- read_csv(here("Literacy Rate.csv"))
  # Literacy processing 1: change space to underbar
  # Literacy processing 2: Order the country alphabetically
  literacy <- literacy |> 
    rename_with(~ str_replace_all(., " ", "_")) |> 
    arrange(Country)
  
job <- read_csv(here("data.csv"))

gdp <- read_csv(here("GDPINT.csv"))

crime <- read_csv(here("crime.csv"))

```


```{r clean, include = FALSE}
# Check there are no duplicate ->> Deleted duplicate Zimbabwe in literacy dataset
length(mbti |> pull(Country) |> unique()) == nrow(mbti)
length(happy |> pull(Country_name) |> unique()) == nrow(happy)
length(literacy |> pull(Country) |> unique()) == nrow(literacy)
  duplicated(literacy$Country) #The last row (Zimbabwe) is duplicate 
  literacy <- literacy[1:174, ] #Remove the row
  length(literacy |> pull(Country) |> unique()) == nrow(literacy) #Verified no duplicate
length(job |> pull(COUNTRY) |> unique()) == nrow(job)
length(gdp |> pull(Country) |> unique()) == nrow(gdp)
length(crime |> pull(country) |> unique()) == nrow(crime)

# Check there are no missing values ->> Missing values in GDP, will check again after merge
sum(is.na(mbti))
sum(is.na(happy))
sum(is.na(literacy))
sum(is.na(job$COUNTRY))
sum(is.na(job$AVG_JOB_SATISFACTION))
sum(is.na(gdp$Country))
sum(is.na(gdp$GDP.2021))
sum(is.na(gdp$GDP.2022))
sum(is.na(gdp$GDP.2023))
sum(is.na(crime$country))

# Check whether the countries are named differently between datasets
# Use countrycode function to assign the uniform countryname
# For GDP, GDP has more comprehensive country names, change column name
mbti <- mbti |> 
  mutate(country_key = countrycode(mbti$Country, "country.name", "iso3c")) |> 
  relocate(country_key, .after = Country)
happy <- happy |> 
  mutate(country_key = countrycode(happy$Country_name, "country.name", "iso3c")) |> 
  relocate(country_key, .after = Country_name)
literacy <- literacy |> 
  mutate(country_key = countrycode(literacy$Country, "country.name", "iso3c")) |> 
  relocate(country_key, .after = Country)
job <- job |> 
  mutate(country_key = countrycode(job$COUNTRY, "country.name", "iso3c")) |> 
  relocate(country_key, .after = COUNTRY)
gdp <- gdp |> 
  rename(country_key = ...2 )
crime <- crime |> 
  mutate(country_key = countrycode(crime$country, "country.name", "iso3c")) |> 
  relocate(country_key, .after = country)

# Confirm if there is any NA value ->> Kosovo is only in happy dataset
# We will extract countries that are icluded in all datasets, so delete the Kosovo row
mbti$Country[is.na(mbti$country_key) == 1]
happy$Country_name[is.na(happy$country_key) == 1]
  happy <- happy |> 
    filter(Country_name != "Kosovo") # delete Kosovo
  happy$Country_name[is.na(happy$country_key) == 1] # double check
literacy$Country[is.na(literacy$country_key) == 1]
job$COUNTRY[is.na(job$country_key) == 1]
gdp$Country[is.na(job$country_key) == 1]
crime$country[is.na(crime$country_key) == 1]

```



```{r reorganize and merge}
# Reorganize mbti dataset
  # Make mbti into pivot
  mbti_wide <- mbti |> 
    pivot_longer(cols = "ESTJ_A":"INFJ_A",
                 names_to = "Category",
                 values_to = "Value")
  
  # Divide category specifically 
  mbti_wide <- mbti_wide |> 
    mutate(E_flag = if_else(substr(Category, 1, 1)=="E", 1, 0),
           S_flag = if_else(substr(Category, 2, 2)=="S", 1, 0),
           T_flag = if_else(substr(Category, 3, 3)=="T", 1, 0),
           J_flag = if_else(substr(Category, 4, 4)=="J", 1, 0),
           A_flag = if_else(substr(Category, 6, 6)=="A", 1, 0))
  
  mbti_summary <- mbti_wide |> 
    group_by(country_key) |> 
    summarise(
      E_prop = sum(Value[E_flag == 1]),
      S_prop = sum(Value[S_flag == 1]),
      T_prop = sum(Value[T_flag == 1]),
      J_prop = sum(Value[J_flag == 1]),
      A_prop = sum(Value[A_flag == 1])
    )

# Reorganize happy dataset: Select only the relevant column in the dataset
happy_summary <- happy |> 
  select(country_key, Ladder_score)

# Reorganize literacy dataset: Select only the relevant column in the dataset
literacy_summary <- literacy |> 
  select(country_key, Literacy_Rate)
  
# Reorganize job dataset: Select only the relevant column in the dataset
job_summary <- job |> 
  select(country_key, AVG_JOB_SATISFACTION)

# Reorganize gdp dataset: Select only the relevant column in the dataset
gdp_summary <- gdp |> 
  select(country_key, GDP.2022)

# Reorganize crime dataset: Select only the relevant column in the dataset
crime_summary <- crime |> 
  select(country_key, crimeIndex)

# Merge datasets
all_data <- list(mbti_summary, happy_summary, literacy_summary, gdp_summary, crime_summary) #, job_summary to be included
mbti_country <- reduce(all_data, inner_join, by = "country_key")
mbti_country <- mbti_country |> 
  mutate(country = countrycode(mbti_country$country_key, "iso3c", "country.name")) |> 
  relocate(country, .before = country_key)
mbti_country
```

```{R plot}
# Examine normality
# Create blank data frame
normality <- data.frame(
  variable = character(0),
  normality = character(0)
)
for(i in 3:ncol(mbti_country)){
  test <- shapiro.test(mbti_country[[i]])
  test_result <- ifelse(test$p.value > 0.05, "Normal", "Not normal")
  normality <- rbind(normality, data.frame(
    variable = colnames(mbti_country[i]),
    normality = test_result
  ))
}
print(normality)
mbti_country_df <- as.data.frame(mbti_country)
# Draw graph with correlation

for(j in 8:ncol(mbti_country_df)){
  for(i in 3:7){
    if(normality[i-2, 2] == "Normal" & normality[j-2, 2] == "Normal"){
      cor_method <- "pearson"  
    } else {
      cor_method <- "spearman"
    }
    
    graph <- ggplot(mbti_country_df, aes(x = .data[[colnames(mbti_country_df)[i]]], 
                                         y = .data[[colnames(mbti_country_df)[j]]])) +
      geom_point() +
      geom_smooth(method = "lm", color = "blue", se = FALSE) +
      labs(
        title = paste0("Correlation between ", colnames(mbti_country_df)[i], " and ",
                       colnames(mbti_country_df)[j], " using ", cor_method, " method"),
        x = colnames(mbti_country_df)[i],
        y = colnames(mbti_country_df)[j]
      ) +
      theme_minimal() +
      stat_cor(method = cor_method)
    print(graph)
  }
}
```

``` {r HeatMap_Keying}

# gdp
gdp_data <- data.frame(
  Country = mbti_country_df$country, # Include all 126 countries
  GDP_Sum = mbti_country_df$GDP.2022)
gdp_data

gdp_wm <- joinCountryData2Map(gdp_data, joinCode = "NAME", nameJoinColumn = "Country")

mapCountryData(gdp_wm, nameColumnToPlot = "GDP_Sum", 
               mapTitle = "Global Distribution of GDP",
               colourPalette = "heat", # You can also try palettes like "terrain", "rainbow"
               oceanCol = "lightblue", # Background color for oceans
               missingCountryCol = "white")

# sensing

S_data <- data.frame(
  Country = mbti_country_df$country,
  S_Sum = mbti_country_df$S_prop)
S_data

S_wm <- joinCountryData2Map(S_data, joinCode = "NAME", nameJoinColumn = "Country")

mapCountryData(S_wm, nameColumnToPlot = "S_Sum", 
               mapTitle = "Global Distribution of GDP",
               colourPalette = "heat", # You can also try palettes like "terrain", "rainbow"
               oceanCol = "lightblue", # Background color for oceans
               missingCountryCol = "white")


